My English activity log

### 2019-11-24 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 24/11/2019

author:
  - name: Aurélie Pinchart
date: 11-04-2019
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

>>>>

author:
  - name: Aurélie Pinchart
date: 11-24-2019
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

20/11/2019 : I watched a video about DNA and RNA https://www.youtube.com/watch?v=JQByjprj_mA.

21/11/2019 : I watched a video about skin https://www.youtube.com/watch?v=b9Fim9kKVLs.

23/11/2019 : I watched a video about reflex arc https://www.youtube.com/watch?v=SMcF01utk3Y.

24/11/2019 : I watched a video about signal transduction pathways https://www.youtube.com/watch?v=236d5LDUFSs and I read the ninth chapter of "The Hobbit".
